---
title: "Multiple Traits"
author: "Grace"
date: "2024-09-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

``` {r echo=FALSE}
library(palmerpenguins)
library(knitr)
library(tidyverse)
```


## Relationship between multiple traits  
Here I will look at the relationship between bill length and depth and how that ratio may vary between different penguin species.  

First, I will just look at the relationship between bill length and depth overall.
```{r bill length:depth}
penguins%>%
  ggplot() +
  geom_point(aes(x=bill_length_mm, y = bill_depth_mm, color = species)) +
  theme_bw() +
  labs(x = "Bill Length (mm)", y = "Bill Depth (mm)", title = "Bill Length vs. Depth in Three Species of Penguin")
```

This graph suggests that Adelie penguins tend to have bills that are more short and deep; that Gentoo penguins tend to have bills that are longer but less deep; and that Chinstrap penguins have beaks with a more balanced ratio between length and depth.


Now I will look at it as a ratio more specifically:  
```{r ratio}
penguins%>%
  ggplot() +
  geom_boxplot(aes(x = species, y = (bill_length_mm/bill_depth_mm))) +
  theme_bw() +
  labs(x = "Penguin Species", y = "Ratio of Bill Length to Bill Depth", title = "Penguin Beak Dimensions by Species")
```
