---
title: "Sexual Dimorphism"
author: "Grace"
date: "2024-09-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


``` {r echo=FALSE}
library(palmerpenguins)
library(knitr)
library(tidyverse)
```


## Sexual dimorphism   
I will investigate the difference in body mass by penguin sex, adding color to illustrate any possible differences in penguin species.  

```{r sexual dimorphism}
penguins%>%
  filter(!is.na(sex)) %>%
  ggplot() + 
  geom_point(aes(x = sex, y = body_mass_g, color = species)) +
  theme_bw() +
  labs(x = "Sex", y = "Body Mass (g)", title = "Variation in Penguin Body Mass by Sex and Species")
```

Because it's hard to see the variation by species here, I'll divide each species into its own graph. Even before doing so, I can see that this initial graph suggests males have a greater body mass than females across species.

```{r}
penguins%>%
  filter(!is.na(sex)) %>%
  ggplot() + 
  geom_density(aes(x = body_mass_g, color = sex)) +
  theme_bw() +
  facet_wrap(~ species, nrow = 1) +
  labs(x = "Body Mass (g)", title = "Variation in Penguin Body Mass by Species and Sex")
```  

Yes - males tend to be larger than females in body mass across species. There is a lot of overlap between them; body mass is unlikely to be helpful in determining penguin sex when used as the only characteristic.